### 2023-03-24 resilience.tex
details

\begin{theorem}\label{down-down}
The resilience problem is undecidable for WSTS with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{theorem}\label{up-down}
\textcolor{red}{
The resilience problem is undecidable for WSTS with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
}
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ \\ \hline
   RP & Decidable (Theorem~\ref{up-up}) & Decidable (Theorem~\ref{down-up}) & Undecidable (Theorem~\ref{down-down}) & \textcolor{red}{Undecidable} \\ \hline
   BRP & Decidable (Corollary~\ref{B-up-up}) &  Decidable (Theorem~\ref{down-up}) & ?? & ?? \\ \hline
      kRP & Decidable (Theorem~\ref{k-up-up}) & \textcolor{red}{Decidable} (Theorem~\ref{k-down-up}) & ?? & ?? \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{theorem}\label{down-down}
The resilience problem is undecidable for WSTS with
%	with more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{theorem}\label{up-down}
\textcolor{red}{
The resilience problem is undecidable for WSTS with 
%	more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
}
\end{theorem}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ \\ \hline
   RP & Decidable (Theorem~\ref{up-up}) & Decidable (Theorem~\ref{down-up}) & Undecidable (Theorem~\ref{down-down}) & \textcolor{red}{Undecidable} \\ \hline
   BRP & Decidable (Corollary~\ref{B-up-up}) &  Decidable (Theorem~\ref{down-up}) & ?? & ?? \\ \hline
      kRP & Decidable (Theorem~\ref{k-up-up}) & Decidable (Theorem~\ref{k-down-up}) & ?? & ?? \\ \hline
 \end{tabular}
\end{center}
